
# Let's get started

To conduct this training you will need to install some tools:

  1. [Download and install R](https://cran.r-project.org)
  2. Download and install an Integrated Development Environment (IDE) in general we use [R studio](https://posit.co/download/rstudio-desktop/), but feel free to use the IDE that you prefer. Other interesting IDEs might be: [Positron](https://positron.posit.co) or [Visual Studio Code](https://code.visualstudio.com/Download).
  3. Make sure you have the required packages installed:

```{r, eval=FALSE}
install.packages("pak")
pak::pkg_install(c(
  "CDMConnector", "CodelistGenerator", "duckdb", "DrugUtilisation", 
  "DrugExposureDiagnostics", "CohortConstructor", "omock", "ggplot2", 
  "visOmopResults", "gt", "usethis", "shiny", "here", "bslib", "DT",
  "shinycssloaders", "shinyWidgets", "plotly", "shinyjs", "CohortSurvival",
  "extrafont"
))
```

  4. Set up your environment:
```{r, eval=FALSE}
library(usethis)
edit_r_environ()
```

Write the path to a folder in your computer to save the mock data:

```
OMOP_DATA_FOLDER = "path/to/my/folder"
```

  5. Restart R
  
  6. Check your data folder has been set properly.
  
```{r, eval=FALSE}
library(omopgenerics)
omopDataFolder()
```

  7. Download *Eunomia* dataset:
  
```{r, eval=FALSE}
library(omock)
downloadMockDataset(datasetName = "GiBleed")
```

  8. Create a reference to the *Eunomia* dataset:

```{r, echo=FALSE}
library(omock)
```
```{r}
cdm <- mockCdmFromDataset(datasetName = "GiBleed")
cdm
```

You are all set :)
